### 2017-01-07 paper/evaluation.tex
updated rq1

\Jbc{Ensure to describe that: I re-executed the experiment 3 times (1
remaining!), subjects that could not run the tests due to incompatible
testing environment were removed (likely to happen for subjects that
rely on database systems and other external factors), the exit status
for all executions are consistent and removed the unstable subjects
(flakiness)}

%% We grouped the subjects according the execution time (in average)
%% using the same criteria of a previous work
%% \cite{gligoric-etal-issta2015}: subjects that run in less than one
%% minute were classified as \emph{short execution} and \emph{long
%% execution} otherwise. Figure~\ref{fig:piechart-time} shows the
%% proportion of subjects per group and figure~\ref{fig:boxplots-time}
%% shows the distribution of elapsed time for each group (boxplots).
%%

\begin{figure}[ht]
    \centering
    \begin{subfigure}{0.21\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/barplot-timecost.pdf}
        \caption{\label{fig:rq1-barplot}}
    \end{subfigure}%
    ~ 
    \begin{subfigure}{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/boxplot-timecost.pdf}
        \caption{\label{fig:rq1-boxplot}}

    \end{subfigure}
    \caption{Caption place holder}
\end{figure}

%% Results indicate that a relatively high number of projects from the
%% sample set (\ie, 29,2\%) requires at least five minutes to execute.
%% The boxplot for the \emph{long} group reveals \Fix{dissect the
%% boxplot: skewness, median, IQR}. \Fix{Discuss outliers from Long
%% group}.  It is important to mention that
%% Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
%% time: some tests may finish early due to a failure since the subjects
%% were tested in a potentially unstable revision.

>>>>

\Jbc{Ensure to describe that: subjects that could not run the tests
due to incompatible testing environment were removed (likely to happen
for subjects that rely on database systems and other external
factors), the exit status for all executions are consistent and
removed the unstable subjects (flakiness)}

We ran each subject's tests three times and grouped them according to
the time cost (in average): tests that run in less than a minute
(\emph{short} group), tests than run in one minute and less than five
minutes (\emph{medium} group), and tests that run in five (or more)
minutes (\emph{long} group). We based our classification from a
previous work \cite{gligoric-etal-issta2015} and added the
\emph{medium} group due to the variability of the time cost from
subjects out of the \emph{short} group. Figure~\ref{fig:rq1-boxplot}
shows the time cost distribution of each group: the \emph{short} group
is the most right skewed distribution with outliers closed to the
\emph{medium} group and 50\% of the subjects run in less than 15
seconds; the average from the \emph{medium} group is nearly two minutes
and most of the subjects run in less than four minutes; most of the
\emph{long} group runs in less than 25 minutes but has outliers that
require more than 50 minutes to execute. Figure~\ref{fig:rq1-barplot}
summarizes the proportion of subjects from each group.

\begin{figure}[ht]
    \centering
    \begin{subfigure}{0.21\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/barplot-timecost.pdf}
        \caption{\label{fig:rq1-barplot}}
    \end{subfigure}%
    ~ 
    \begin{subfigure}{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/boxplot-timecost.pdf}
        \caption{\label{fig:rq1-boxplot}}
    \end{subfigure}%
    \caption{(a) Subjects grouped by time cost ($t$): short run ($t <
    1m$), medium run ($1m \le t < 5m$), and long run ($5m \le t$); (b)
    Distribution of time cost by group.}
\end{figure}

Given that 19.3\% of the projects (\ie, \Fix{X} projects) are costly,
we concluded that time-consuming regression test suites are relatively
frequent in open-source projects.  It is important to mention that
Figure~\ref{fig:rq1-barplot} represents a lower bound for time cost:
some tests may finish early due to a failure since the subjects were
tested in a potentially unstable revision. \Jbc{How many executed
completely? From the failed subjects, how much of the test suite was
executed?}
